|

### 2022-01-19 curve-fitting-methods/curve-fitting-scratch.Rmd
minor tweaks

```{r, fig.width = 8}
relations.df <- readr::read_csv('~/dev/potter-network/data/relations.csv') %>% 
  dplyr::mutate(source = source + 1, target = target + 1)
characters.df <- readr::read_csv('~/dev/potter-network/data/characters.csv') %>% 
  dplyr::mutate(id = id + 1)
n <- nrow(characters.df)

@@

z.init <- kmeans(sweep(Xhat, 1, apply(Xhat, 1, function(x) sqrt(sum(x ^ 2))), `/`), 2)$cluster
```

```{r, fig.width = 10, fig.height = 4, cache = TRUE}
manifold.out <- manifold.clustering.quadr.2(A, 2, p = 1, q = 1, 
                                            initialization = z.init, 
                                            eps.isomap = .7,
                                            method = 'bezier')

@@

>>>>

```{r, fig.width = 4, fig.cap = 'Labels based on output of disassortative DCBM clustering'}
relations.df <- readr::read_csv('~/dev/potter-network/data/relations.csv') %>% 
  dplyr::mutate(source = source + 1, target = target + 1)
characters.df <- readr::read_csv('~/dev/potter-network/data/characters.csv') %>% 
  dplyr::mutate(id = id + 1)
n <- nrow(characters.df)

@@

z.init <- kmeans(sweep(Xhat, 1, apply(Xhat, 1, function(x) sqrt(sum(x ^ 2))), `/`), 2)$cluster

qgraph::qgraph(A, groups = factor(z.init))
```

```{r, fig.width = 10, fig.height = 4, cache = TRUE}
manifold.out <- manifold.clustering.quadr.2(A, 2, p = 1, q = 1, 
                                            # initialization = z.init, 
                                            eps.isomap = .7,
                                            intercept = FALSE)

@@

t. <- seq(0, 1, .01)
theta1 <- manifold.out$theta[[1]]
theta2 <- manifold.out$theta[[2]]
Y1 <- param.curve.quadr.2(t., 
                          theta1[1], theta1[2], theta1[3], 
                          theta1[4], theta1[5], theta1[6])
Y2 <- param.curve.quadr.2(t.,
                          theta2[1], theta2[2], theta2[3],
                          theta2[4], theta2[5], theta2[6])
Y <- rbind(Y1, Y2)
z. <- c(rep(1, length(t.)),
        rep(2, length(t.)))
Y <- rbind(manifold.out$X[[1]], manifold.out$X[[2]])
z. <- sort(zhat.manifold)
